Synthesizing Verified Components~~~\\ for Cyber Assured Systems Engineering~ \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2021-08-01 paper/case-study.tex
Updated intro and case-study with more detailed scope

In this section, we outline the application of the BriefCASE tool towards the development of a UAV surveillance system as a part of the DARPA CASE program.
%apply the BriefCASE tool towards the development of a UAV surveillance system in which 
The UAV receives commands from a ground station to conduct surveillance over a geographical region. In response, the UAV's on-board mission computer generates a flight plan consisting of a series of waypoints that the UAV must traverse to complete its mission. The UAV is also given a set of \textit{keep-in} and \textit{keep-out} zones that may constrain its flight path.

>>>>

In this section, we outline the application of the BriefCASE tool towards the development of a UAV surveillance system as a part of the DARPA CASE program.
The motivation here was to showcase the toolchain on an industrial scale problem, to see if the technology works, i.e. provides engineers with early validation of their model; provides early information about cyber-vulnerabilities and in the effectiveness of related mitigations; to show that the tool can handle the UXAS message format (a complex, real-world message format); and to validate the utility and capability of the toolchain.

%apply the BriefCASE tool towards the development of a UAV surveillance system in which 
The UAV receives commands from a ground station to conduct surveillance over a geographical region. In response, the UAV's on-board mission computer generates a flight plan consisting of a series of waypoints that the UAV must traverse to complete its mission. The UAV is also given a set of \textit{keep-in} and \textit{keep-out} zones that may constrain its flight path.

### 2021-08-01 paper/intro.tex
Updated intro and case-study with more detailed scope

>>>>

CASE was scoped to address the more common cyber-vulnerabilities that programmers introduce, such as overflow, lack of input validation, supply-chain issues, and identity verification; and not cyber-vulnerabilities such as side-channel attacks and denial of service.
In this program, we have not invented a new type of filter or monitor in terms of capability, instead our contribution is in the automated synthesis of these components from a formal specification, and a means to show that the synthesis is correct.
